### 2023-02-20 paper/content.tex
Finish adding the full paper text to the repository

>>>>

\subsection{Complex simulation: Testing applicability}

This test represents a more complex scenario by simulating 100 sources randomly
distributed in the imaged area of a synthetic thin section of 2000 x 1400 $\mu
m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$
spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real
samples, the magnetic sources are modeled as spheres with different depths,
radii, and magnetizations. The depths vary between 1 and 19 $\mu m$, while the
radii range from 0.01 to 0.95 $\mu m$. The magnetizations of the sources have
declination and inclination directions sampled from a pseudo-random Gaussian
distribution with a mean of D, I = 45°, 45°, and a standard deviation of 8°.
This randomness simulates the NRM found in real ferromagnetic particles that
vary individually but average out to the inducing field direction. Finally, we
contaminated the data with high-frequency normally-distributed pseudo-random
noise with zero means and 5 nT standard deviations, as well as with
low-frequency noise in the form of additional deep sources beyond the modeling
domain. The noise-corrupted synthetic $b_z$ image is shown in
Figure~\ref{E9td9j9aBB}a.

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
\label{e9td9j9abb}
\end{figure}

The result of the source detection method is shown in Figure~\ref{E9td9j9aBB}b,
where 84 particles out of the original 100 were detected. The spatiality of the
inversion results is one of the key advantages of magnetic microscopy over the
classic techniques of paleomagnetism. Therefore, we present the inversion
results spatially so that we can evaluate any patterns in their distribution.

Figure~\ref{P8gMJ9mWpS} shows the difference between the estimated dipole
moments and the true values for each of the 84 particles that were identified.
Figure~\ref{P8gMJ9mWpS}c shows the R² coefficient of determination representing
how well the dipolar model is able to fit the observed data in the given
window. The depth and radius of each particle are represented by horizontal and
vertical cross bars, respectively. The depth and radius are useful proxies for
the width and amplitude of the magnetic signal of each particle, which is
crucial to know when evaluating the inversion results.

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexComparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for
each individual particle based on the error between the real parameters modeled
and their respective recovered values, being (a) the direction and (b)
intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
by comparing the forward model and the actual data. The depth and radius of the
magnetic sources are also important factors that influence the final result,
therefore, these data are given in the form of cross plots, with the vertical
bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
radius (0.01 - 0.95 $\\mu m$).
}
\label{p8gmj9mwps}
\end{figure}

The application in complex synthetic data allows observing the strengths and
limitations of the proposed methodology. Some of the strengths that can be
mentioned are: (i) the applied technique not only detects most of the modeled
sources but also (ii) most of the recovered magnetic parameters have
considerably low errors, especially in the directions, usually less than 5°
(Figure~\ref{P8gMJ9mWpS}a). (iii) The magnetic moments obtained also tend to
not deviate much from the real values (Figure~\ref{P8gMJ9mWpS}b) when
R\textsuperscript{2} scores are high (\textgreater 0.95)
(Figure~\ref{P8gMJ9mWpS}c). (iv) Shallow particles grouped in clusters are
usually well individualized during window selection, as well as (v) some
particles that produce a weak magnetic signal but isolated particles.

The main limitations observed are: (i) the blob detection fails when there are
sources too close, grouping them into the same window, thus causing an
erroneous result both for Euler deconvolution and for the magnetic parameters.
(ii) The very same occurs when there is a source under another, in this case,
the magnetic signal is the sum of both. (iii) In clusters of larger and/or
deeper particles, although the method individualizes them well, the magnetic
signal of the neighboring particles can considerably influence the result of
the inversion. Apparently, there is a direct relationship between the size and
depth with the observed errors. It is clear from the cross bars in
Figure~\ref{P8gMJ9mWpS} that deep particles and/or particles with small radii
generate worse results essentially because they will produce smaller anomalous
fields in the magnetic maps. Note nonetheless that even small particles when
close to the surface are adequately modeled by our method.

Figure~\ref{RDs2vUEqCI} shows stereoplots with the directions generated by the
model and the recovered data. The mean directions modeled are coincident with
the model and the distribution is coincident within the 95\% confidence cone.
When filtered to include only data with R\textsuperscript{2} \textgreater 0.95
the obtained directions are closer to the model average and less sparse.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexStereo.png}
\caption{
a) Simulation of a thin section of rock with particles uniformly magnetized in
the average direction of the induced field
45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
data, without any type of filtering, are sparse, but statistically generate the
same average direction. c) It is still possible to filter only the directions
of the magnetic sources with the best fitting determined by the coefficient of
determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
around the mean value.
}
\label{rds2vueqci}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to real data}

To test whether the proposed method would be able to determine the
magnetization directions and the magnetic moment of particles in natural
samples, we selected a previously studied carbonate stalagmite sample from the
Wintimdouine cave in the Agadir region (Morocco) \citep{Ait2019Hydro}. This
speleothem contains both magnetite and hematite as the main carriers of
magnetic remanence, as attested by thermomagnetic curves with temperature
decays at {\textasciitilde}580 °C and {\textasciitilde}680 °C, and bimodal
curves of isothermal remanent magnetization (IRM) acquisition (Carmo et al.,
2019).

In order to provide two distinct directions associated with the different
magnetic mineral types in this sample, we applied two IRM pulse fields of 2.7 T
and 0.3 T, respectively toward the +X and -X directions. In this way, the high
coercivity grains (hematite) would point towards +X and the low coercivity ones
(magnetite) would align in the -X direction.

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{W1GfysVYnX}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 85 potential sources
(Figure~\ref{W1GfysVYnX}b).

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealData.png}
\caption{
a) Real sample data. b) Individual sources' window position (yellow squares)
obtained with the blob detection algorithm applied on the total gradient map.
}
\label{w1gfysvynx}
\end{figure}

After applying the ED algorithm, we performed the inversion of the magnetic
moment for each of the 85 windows selected previously. In order to reduce
considerably the computation time, the inversions were done within each data
window, instead of solving all sources parameters at the same time. We obtained
the magnetic moment (not shown) and the direction for all 85 magnetic grains
(Figure~\ref{NKOAMThaWA}a). Then, we calculated the residuals of the inversions
in each window and subsequently the coefficient of determination
R\textsuperscript{2}, which was used as a filter for the best directions
obtained. We used a cut-off limit of the coefficient of determination at 0.7
(Figure~\ref{NKOAMThaWA}b) EXPLICAR PORQUE USOU 0.7 AQUI E 0.95 NOS CASOS
SINTÉTICOS. This filtering technique removed unreliable responses showing more
clearly the expected directional clusters of hematite and magnetite crystals.
NÃO SABEMOS SE OS PONTOS RETIRADOS SÃO `UNRELIABLE RESPONSES'\dots ALÉM DISSO,
O FILTRO ELIMINA QUASE 50\% DAS FONTES IDENTIFICADAS, O QUE PODE SER UM
PROBLEMA SE TIVERMOS QUE APLICAR EM OUTROS CASOS REAIS. USAR O TESTE DE
NÃO-DIPOLARIDADE? TALVEZ SEJA MAIS INTERESSANTE, DADA A DISCUSSÃO QUE SEGUE.

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
\caption{
a) The recovered data, without any type of filtering. b) Recovered data
filtered by the coefficient of determination ($R^ 2 \\geq 0.7$), which shows
two clusters of direction located on each pole of the stereogram.
}
\label{nkoamthawa}
\end{figure}

NESSA PARTE SERIA INTERESSANTE INCLUIR MAPAS COMO OS DA FIGURA 4B E 4C, COM A
ESPACIALIDADE DOS AJUSTES E DISCUTIR DA SEGUINTE FORMA:

\begin{enumerate}
\item RESULTADOS EM FUNÇÃO DA QUALIDADE DO AJUSTE
\item RESULTADOS EM FUNÇÃO DA DIPOLARIDADE DAS FONTES
\item CONTEXTUALIZAR O SEU MÉTODO EM RELAÇÃO A OUTROS. COMO OS OUTROS ESTIMAM
  OS MISFITS? QUE FILTROS USAM? QUAL A DIFERENÇA COM SUA ABORDAGEM? POR
  ENQUANTO SOMENTE O TRABALHO DE CORTEZ ESTÁ COMENTADO -> COMPARAR COM
  OS OUTROS MÉTODOS DE INVERSÃO (Fu, de Groot, Egli2000, Lima2007)
\end{enumerate}

The application of the proposed algorithm to natural samples gives some
indications of its ability to circumvent the prominent problems described by
\citep{CortesOrtuno2022} [QUAIS PROBLEMAS FORAM LISTADOS POR CORTÉS-ORTUÑO?],
namely: (i)\dots, (ii)\dots, (iii)\dots

the same authors showed that particles in the single vortex PSD state present
more accurate inversion results when considering the non-dipole components for
small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
distances the dipole as approximations are remarkably accurate, as the
higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal. Thus, our approach can be
considered reasonable for working with particle signals in SD (already a
dipole) and PSD states. The latter happens due to the QDM sensor height being
usually greater than 5 $\\mu m$, considering a particle on the immediate
surface of the sample the higher-order moments are already quite attenuated.\}

Despite the excellent signal/noise ratio that the SMM provided with the
proximity of the sensor to the sample, it is worth mentioning that the
measurement noise can still overshadow the responses of very weak/small, or
deep particles, generating unreliable inversion results. Therefore, it is
necessary to keep a check to determine if the inversion reached a satisfactory
result, such as the coefficient of determination that we used or the
signal-to-noise ratio presented by \citep{CortesOrtuno2022}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

We developed an efficient semi-automated method to determine the direction of
magnetization of dipolar sources on a microscale, as well as the recovery of
their magnetic moment. Being ideal for a reinterpretation for the application
of methods of paleomagnetic studies using thin sections of rock samples. This
would be an attempt to improve the quality of results obtained by isolating the
responses of more reliable recorders of the Earth's geomagnetic field.

We also present a new, faster, and cleaner way to solve the Euler equation in
determining the positioning of magnetic anomaly sources using a pre-selection
of magnetic anomaly source windows based on the Laplacian of the Gaussian
applied to total gradient anomaly maps. In this way, reducing the numerous
solutions to just one data window per source. After estimating the structural
index ($n = 3$) by approximating the sources generating the magnetic anomaly to
spheres/points, the Euler deconvolution is performed and the central position
of each source is determined.

The recovery of direction and magnetization we only need to assume that the
sources have their central positions known (so we apply Euler deconvolution)
and that their magnetizations are uniform. This last premise aligns with the
theory of magnetically stable particles SD (and the PSD ones at a reasonable
sensor height), which is the basis of classical paleomagnetism. Also, there is
no need for any kind of prior knowledge other than the observed magnetic
anomaly, and the structural index of the sources. Therefore, this method can be
quickly replicated in a dataset of thin sections of rocks to obtain the
distributions of magnetic directions of each source identified in the sample.

The test using a simple synthetic sample shows the great capability of the
method by retrieving not only the precise center positions, but also retrieving
the magnetization directions and intensity even under the considerable effect
of high-frequency noise (15 nT). While the complex synthetic sample data allows
observing the applicability of the method developed in real samples that are
more complex with varied magnetization directions and intensity, in addition to
also taking into account the high and low-frequency noise and sources with
variable sizes and depths.

The real sample data positively answered the question of the algorithm's
ability to deal with rocks thin-sections. But also, showed the acceptable
capacity (within the adequate R$^2$ threshold) of retrieving different
magnetization directions recorded by magnetic minerals with different
coercivities and magnetic signal disparities even greater than predicted in the
complex synthetic test.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data and code availability}

The Python source code used to produce all results and figures presented here
is available at \url{https://github.com/\GitHubRepository} and
\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.

The image rescaling and blob detection though the Laplacian of Gaussian method
were performed with the scikit-image library \citep{VanderWalt2014}. CITE OTHER
SOFTWARE TOOLS USED. Matplotlib for figures, numpy and scipy for almost
everything. Verde for the regional residual separation and other things.

The QDM image data is available at CITE A DATAVERSE/FIGSHARE ARCHIVE under the
CC-XX license.
